\section{METHODOLOGY}\label{Sec:proposal===}
This paper proposed using visual and touch sensors only to perform the automatic pick and place grasping task in a constrained environment with given surfaces and initial location of the hindering object. The visual sensor used in the study is a RGB-D camera and the touch sensors used are bumpers. Both are for object detection purpose. We proposed to extract a three-dimensional point cloud of the cylinder using RGB-D camera. We decided to use the PCL mentioned earlier for point cloud processing and object segmentation and extraction. We applied various filters such as voxel-grid, which uses clustering to down sample the size of the point clouds, and pass through filters, which filter out points irrelevant to the objects we are interested, to reduce the number of points in the cloud. As the  extraction of the location and height of the cylinder needs to go through every point in the cloud, decreasing the number of points lowers the computational complexity of cylinder extraction. 

We then use model based extraction methods to extract and remove the plan surface to facilitate extraction of cylinder. A mathematical approach is taken to calculate the normal of the remaining points to find the points with similar normal as the cylinder to extract the cylinder. Following that, the extracted normal is used to extract the cylinder using model based extraction with mathematical parameters of an infinite cylinder. The height of the cylinder is determined using the coordinates of the highest and the lowest point in the point cloud. 

After the cylinder is detected, we keep track of the latest cylinder pose. We also detect and track whether the surface that cylinder is supposed to be moved to is free from any other object by using bumper sensors. Each surface has a bumper sensor located at the centre that notifies whether the surface is occupied. If occupied, a pick-and-place is performed to move the object to some other unoccupied table before placing the cylinder. The robot only receives which surface to put the cylinder as input information from the users, and perform the rest of the tasks automatically. Hence, Our proposed algorithm needs to handle the detection of any object on the designated table, clearing of the object and pick-and-place of cylinder to transport it to the designated surface. The details of the experimental setup and the simulations are introduced in section \ref{sec:exp}. 